MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-03-12 MAESTROeX_I/paper.tex
added some advection references; moved stuff to appendix B (notes that won't make the final paper) also testing email notification to maestro-development

Using equation (\ref{eq:momentum}), 
we compute time-centered edge velocities, $\uadvonedag$, using
$\Ub^n$.  The $\dagger$ superscript refers to the
fact that the predicted velocity field does not satisfy the divergence
constraint.  We then construct $\uadvone$ from $\uadvonedag$
using a MAC projection.
We note that $\uadvone$ satisfies the divergence constraint
\begin{equation}
\nabla \cdot \left(\beta_0^n \uadvone\right) = \beta_0^n \left(S^{\nph,\star} - \frac{1}{\gammaonebar^np_0^n}\frac{\partial p_0}{\partial t} \right).
\end{equation}
In practice we solve for.

@@

\item Define a radial cell-centered $\etarho^{\nph}$.

@@

\subsection{Computing $w_0$ For Spherical Problems}
Recall that we want to solve
\begin{equation}
\frac{1}{r^2}\frac{\partial}{\partial r}(r^2 w_0) = \Sbar - \frac{1}{\gammaonebar p_0}\left(\frac{\partial p_0}{\partial t} + w_0\frac{\partial p_0}{\partial r}\right)
\end{equation}
First, note that $\partial p_0/\partial r = -\rho_0 g$.
The key observation here is that we can compute $\partial p_0/\partial t$ directly instead of making complicated substitutions involving $\eta_\rho$ to eliminate it.
Let's discretize this as follows:
\begin{equation}
\frac{1}{r_j^2}\left[\left(r^2 w_0\right)_{j+\myhalf} - \left(r^2 w_0\right)_{j-\myhalf}\right] = 
\Sbar_j - \frac{1}{\left(\gammaonebar p_0\right)_j}\left[\left(\frac{\partial p_0}{\partial t}\right)_j - \left(\frac{w_{0,j-\myhalf}+w_{0,j+\myhalf}}{2}\right)(\rho_0 g)_j\right]
\end{equation}
Rearranging this to solve for $w_{0,j+\myhalf}$ gives us an explicit update:
\begin{equation}
\left[\frac{r_{j+\myhalf}^2}{r_j^2} - \frac{(\rho_0 g)_j}{2\left(\gammaonebar p_0\right)_j}\right] w_{0,j+\myhalf} =
\left[\frac{r_{j-\myhalf}^2}{r_j^2} + \frac{(\rho_0 g)_j}{2\left(\gammaonebar p_0\right)_j}\right] w_{0,j-\myhalf}
+ \Sbar_j - \frac{1}{\left(\gammaonebar p_0\right)_j}\left(\frac{\partial p_0}{\partial t}\right)_j
\end{equation}
As before, once $\rho_0$ falls below $\rho_{\rm cutoff}$, we hold $r^2 w_0$ constant.\\ \\
The interface to the routine in the algorithm description is
{\bf Make $\mathbf{w_0}$}$[\rho_0,p_0,\partial p_0/\partial t,\gammaonebar,\Sbar] \rightarrow [w_0]$

@@

>>>>

The construction of face-centered time-centered states used to discretize the
advection terms for velocity, species, and enthalpy, are performed using
standard multidimensional corner transport upwind 
\cite{colella1990multidimensional,saltzman1994unsplit} with piecewise-parabolic
one-dimensional tracing \cite{colella1984piecewise}.  In this step,
using equation (\ref{eq:momentum}), 
we compute time-centered edge velocities, $\uadvonedag$, using
$\Ub^n$.  The $\dagger$ superscript refers to the
fact that the predicted velocity field does not satisfy the divergence
constraint.  We then construct $\uadvone$ from $\uadvonedag$
using a MAC projection.
We note that $\uadvone$ satisfies the divergence constraint
\begin{equation}
\nabla \cdot \left(\beta_0^n \uadvone\right) = \beta_0^n \left(S^{\nph,\star} - \frac{1}{\gammaonebar^np_0^n}\frac{\partial p_0}{\partial t} \right).
\end{equation}
In practice we solve for.

@@

@@

@@

\appendix
\section{Projection Details}

After {\bf Step 8D}, we define a radial cell-centered $\etarho^{\nph}$.

\section{Old Notes}

\section{Computing $w_0$ For Spherical Problems}
Recall that we want to solve
\begin{equation}
\frac{1}{r^2}\frac{\partial}{\partial r}(r^2 w_0) = \Sbar - \frac{1}{\gammaonebar p_0}\left(\frac{\partial p_0}{\partial t} + w_0\frac{\partial p_0}{\partial r}\right)
\end{equation}
First, note that $\partial p_0/\partial r = -\rho_0 g$.
The key observation here is that we can compute $\partial p_0/\partial t$ directly instead of making complicated substitutions involving $\eta_\rho$ to eliminate it.
Let's discretize this as follows:
\begin{equation}
\frac{1}{r_j^2}\left[\left(r^2 w_0\right)_{j+\myhalf} - \left(r^2 w_0\right)_{j-\myhalf}\right] = 
\Sbar_j - \frac{1}{\left(\gammaonebar p_0\right)_j}\left[\left(\frac{\partial p_0}{\partial t}\right)_j - \left(\frac{w_{0,j-\myhalf}+w_{0,j+\myhalf}}{2}\right)(\rho_0 g)_j\right]
\end{equation}
Rearranging this to solve for $w_{0,j+\myhalf}$ gives us an explicit update:
\begin{equation}
\left[\frac{r_{j+\myhalf}^2}{r_j^2} - \frac{(\rho_0 g)_j}{2\left(\gammaonebar p_0\right)_j}\right] w_{0,j+\myhalf} =
\left[\frac{r_{j-\myhalf}^2}{r_j^2} + \frac{(\rho_0 g)_j}{2\left(\gammaonebar p_0\right)_j}\right] w_{0,j-\myhalf}
+ \Sbar_j - \frac{1}{\left(\gammaonebar p_0\right)_j}\left(\frac{\partial p_0}{\partial t}\right)_j
\end{equation}
As before, once $\rho_0$ falls below $\rho_{\rm cutoff}$, we hold $r^2 w_0$ constant.\\ \\
The interface to the routine in the algorithm description is
{\bf Make $\mathbf{w_0}$}$[\rho_0,p_0,\partial p_0/\partial t,\gammaonebar,\Sbar] \rightarrow [w_0]$
